The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-10-01 manuscript.Rmd
include PS edits

With increasing impact of human activities on the biosphere, we need efficient and accurate approaches to document changes in species ranges and community composition. <!-- add why? -->  While terrestrial ecosystems have received considerable attention, the baseline of healthy and resilient marine ecosystems are not well understood [@Worm2006], and modeling the impact of human activities has been limited to a few taxonomic groups [@Tittensor2010]. For marine organisms, because of the diversity of their complex life history strategies, their size range, and the difficulties associated with sampling their habitats, we have limited information about which species live where, or what portion of their diversity remains to be discovered and described [@Mora2011]. Additionally, coordinated marine ecosystem monitoring initiatives have been lacking [@Duffy2013,@Borja2016] (but are now getting organized, see MarineGEO [@Duffy2016marinegeo], MBON, and PISCO), making it difficult to monitor changes in species distributions and abundances. While most documented global extinctions of marine species are vertebrates, many others species may have been lost unnoticed because they were not known [@Sala2006]. There is therefore a pressing need to improve our knowledge of marine systems before their functioning are irreversibly altered, and species go extinct.

Research attempting to understand how much we know about marine biodiversity has focused on estimating the total number of species that inhabits the oceans, and which fraction of this diversity has been named [@Appeltans2012,@Costello2013]. Undoubtedly, the development of molecular methods to investigate species limits has reinvigorated taxonomy, and contributed to elucidating cryptic species complexes [@Knowlton2000]. Thus, it has been argued that molecular data can speed up the enterprise of discovering and naming species [@Blaxter2016]. As species remain the most convenient unit to measure biological diversity, understanding how much has been done, how much remains to be done, and how we can speed up the description of species diversity is crucial. However, to understand the role of these species in their environment, we need to document their ecology [@Cernansky2017]. For instance, to be able to predict how their geographic ranges will be affected by global change, we need detailed information about their environmental requirements. Occurrence data for marine species could be used for environmental niche modeling of their geographic and bathymetric distributions but the proportion of species for which we have enough data to do so is unknown.

Until very recently, our knowledge of biodiversity was scattered among heterogeneous sources (e.g. natural history collections, publications, expert knowledge), difficult to access, and therefore difficult to synthesize. The development of public databases for specimen records (e.g. iDigBio [@Page2015]), species occurrences (e.g., OBIS [@Zhang2002]), genetic data (e.g., GenBank [@Benson2013], BOLD [@Ratnasingham2007a]), and registers of species names (e.g., WoRMS [@Costello2013b]), now allow us to evaluate what and how much we know. However, few studies have sought to synthesize existing knowledge by combining information from these databases.  Here, we aggregate publicly available data for marine invertebrates that occur within the limits of the exclusive economic zone (EEZ) of the continental United States (US), as well as the Gulf of Mexico (GOM) and the Pacific Northwest (PNW), to highlight gaps in our knowledge that provide a road map for important new directions in global research. We show that while public databases are capturing a significant portion of our knowledge about species richness, most species are known from only a few specimens and a few locations. We emphasize that our understanding of marine biodiversity, and the impact of human activities on biological communities require not only a more accurate list of the species that inhabits the oceans, but also more comprehensive data on species distributions and abundances. These goals can only be achieved with additional cost-effective sampling, and a commitment to training more taxonomists and experts that can identify and interpret the material collected.

@@

We retrieved `r format(n_distinct(combined_species$worms_valid_name), big.mark = ",")` species (`r n_distinct(na.omit(combined_species$worms_phylum))` phyla) of marine invertebrates in the continental US EEZ by combining  `r format(nrow(idigbio_records), big.mark=",")` museum records from iDigBio (`r format(n_distinct(idigbio_records$worms_valid_name), big.mark = ",")` species, `r n_distinct(na.omit(idigbio_records$worms_phylum))` phyla), and `r format(nrow(obis_records), big.mark=",")` records from OBIS (`r format(n_distinct(obis_records$worms_valid_name), big.mark=",")` species,
`r n_distinct(na.omit(obis_records$worms_phylum))` phyla). Extant marine invertebrates occurring in the US represent less than 0.4% of the total number of iDigBio records (106 million), and about 1% of the US records (33 million records). Marine invertebrates that occur in the US represent approximately 4% of the 48 million occurrence records in OBIS.

@@

Spatial distribution of species richness with latitude differ markedly between the Pacific and the Atlantic coasts. On the Pacific coast, richness is lowest around 40° of latitude, while it is where it is the highest on the Atlantic coast (Fig. \@ref(fig:map-diversity-sampling)B, Fig. \@ref(fig:latitudinal-gradient)).

@@

```{r correlation-sampling, fig.cap='Relation between number of records and number of species for each cell of the map used in Fig. \\@ref(fig:map-diversity-sampling). The black line represents the 1:1 relation. (\\#fig:correlation-sampling)'}
knitr::include_graphics("figures/plot_sampling_effort.pdf")
```

The median number of cells occupied by species is `r median(rastercell_distribution$n_cell)`.

@@

Environmental conditions are among the primary determinants of species distributions and can thus be used to estimate the response of organisms to climate change. Predictive ecological models forecasting changes in distributions are trained on environmental conditions encountered by species in their current distributions. To obtain reliable results, models require at least 10, but ideally 30 or more occurrence records per species [@Wisz2008]. Yet at present, `r prop_10_specimens_species`% of species are represented by $\leq$ 10 records, and `r prop_30_specimens_species`%  by $\leq$ 30 records based on the combined records in iDigBio and OBIS. Underscoring the inadequacy of the sampling effort, `r prop_singleton_species`% of the species are known from a single record.

Another indication of the inadequacy of the sampling is the relation between the number of collected specimen and the number of species recorded through time (Fig. \@ref(fig:idigbio-through-time)). Explorations in the late ninetieth century led to an exponential growth in the knowledge of the fauna, that tapered off, until the 1970s when intensive collecting efforts led to an increase in the recording of new taxa (Fig. \@ref(fig:idigbio-through-time)). Since then, the slowing down of collections has been accompanied with a slowing down in the discovery of new records: `r n_spp_comparison$n_spp_2017_2000` species have been documented for the first time since 2000 (`r format_output(n_spp_comparison$n_spp_2017_2000/18)` species.year^-1^), while `r n_spp_comparison$n_spp_1970_1960` have been documented between 1960 and 1970 (`r format_output(n_spp_comparison$n_spp_1970_1960/11)` species.year^-1^). The strong correlations between (1) the number of samples collected and the species richness (Fig. \@ref(fig:correlation-sampling)), and (2) the number of specimens collected per year and the number of species recorded for the first time (Fig. \@ref(fig:idigbio-through-time)C), suggest that any new sampling effort will lead to new observations and new species.

```{r idigbio-through-time, fig.cap='Cumulative number of samples (A) and species (B) of marine invertebrates recorded through time based on iDigBio records. Relation between number of samples collected, and number of species recorded for the first time (C), each point represents numbers for a given year, dashed line show the 1:1 and dotted line the 1:100 ratios for number of species recorded for the first time to the number of samples. (\\#fig:idigbio-through-time)'}
knitr::include_graphics("figures/idigbio_through_time.pdf")
```

Further biases exist across phyla and body size. Large-bodied and easily accessible (e.g. dried specimens like shells, corals, echinoderms) are over-represented in museum collections, compared with small less accessible organisms, such as the meiofauna. Of `r n_idigbio_phyla` phyla represented in iDigBio, `r records_rare_phyla$n_rare_phyla` have <500 records, and make up `r records_rare_phyla$prop_recs_rare_phyla`% of the iDigBio records. This under-representation is also manifested at the species level, while `r records_rare_phyla$prop_spp_rare_phyla_collected`% (n = `r format(records_rare_phyla$total_spp_rare_phyla_collected, big.mark=",")` total species) of the global number of species for these `r records_rare_phyla$n_rare_phyla` phyla occur in iDigBio, this proportion rises to `r records_rare_phyla$prop_spp_common_phyla_collected`% (n = `r format(records_rare_phyla$total_spp_common_phyla_collected, big.mark=",")`) for the `r n_idigbio_phyla - records_rare_phyla$n_rare_phyla` others. Yet, these undersampled taxa, especially those of small body size, are often the most abundant, and are likely to play an important role in the detection of changes in environmental quality[@Bik2012]. Additionally, the ecological implications of changes in the structure and composition of the communities of these small-bodied organisms, on higher trophic levels and ecosystems are largely unexplored.

@@

```{r id_though_time, fig.cap='Proportion of marine invertebrate specimens collected through time identified at the species level. Trend lines are  B-splines of the 3rd degree polynomial. For all groups, we observe a decline in the proportion of specimens collected identified at the species level. (\\#fig:identification-through-time)'}
knitr::include_graphics("figures/idigbio_identification_level_through_time.pdf")
```

@@

Since its introduction in the early 2000s, DNA barcoding, has revitalized taxonomy by facilitating species delineation [@Meyer2005-plos]. More recently, advances in high-throughput sequencing technologies have enabled the parallel sequencing of thousands of specimens in environmental samples (eDNA) cost effectively [@Leray2015], making it possible to estimate diversity and identify taxa from species-rich samples at unprecedented scales. With decreasing sequencing costs, and the prospect of automating sample collection, these technologies may soon be used routinely to monitor biodiversity continuously [@Bohan2017]. However, the utility of the data generated by these projects is limited by the paucity of reliably identified DNA barcode sequences that can serve for matching and identification of eDNA transcripts [@Leray2015]. Thus insights from eDNA technologies depend on the level of completeness and accuracy of comparative, species-level DNA barcode coverage.

@@

Based on the results of this study, we recommend a multi-level approach for both improving the quality of existing data, as well as for the efficient collection of new data.

@@

With data aggregation of natural history collections through initiatives like iDigBio, and the compilation of a nearly complete register of marine species with WoRMS, in combination with the development of algorithms for text analysis, it is increasingly easier to validate and spell check the scientific names of the identifications of digitized museum specimens. Linking species names to identifiers in taxonomic databases would facilitate data linking, specimen discoverability, and data usability. Additionally, because species name registers like WoRMS link the history of the names and their synonymies, it is possible to dissociate the concepts of species identification with the concept of species identity, allowing researchers to compare specimens identified at different time periods.

@@

For both the spelling of scientific names, and the geographic information, computing tools can be developed to detect issues and propose solutions. There are opportunities to develop computing services that use publicly available data to flag and fix these issues directly from collection databases records (e.g. see [@Otegui2016] for vertebrate records). It however requires that resources are made available to museum collections in order to address these issues directly in collection databases.

Increasing the computing literacy and teaching "data wrangling" skills to staff of museums in order for them to manipulate and use the data from their collection database is equally critical. As data across institutions get incorporated and pooled into large biodiversity information systems, it is crucial that data standards such as Darwin Core are embraced by the community.

@@

Museum specimens are critical to validate the occurrence of species [@Rocha2014], especially for marine invertebrates for which species limits based on morphology have been known to be challenged by other lines of evidence including molecular data [@Knowlton2000].

This study highlights that we have too little data about too few species of marine invertebrates. We recommend that additional coordinated field expeditions are organized to sample more comprehensively the marine environment. The relation between sampling effort and diversity from museum collections makes clear that any additional samples will greatly improve our knowledge of marine biodiversity. Concerted and collaborative efforts are needed to share expertise and limited resources.

Samples collected during these expeditions need to be photographed to document live appearance that would otherwise be lost during the preservation process. We also need to capture metadata associated with specimens to be able to understand better the physical characteristics of the habitats and the life history for these species. Specimens need to be sub-sampled to create material suitable for genomic analysis. Parts of data acquisition associated with specimens and their biota can be automated and captured digitally directly in the field, speeding up their ingestion in database collections.

Integrating metabarcoding as part of the data collection conducted in biodiversity surveys is a promising approach to screen an habitat for its potential to lead to new discoveries. For instance, by analyzing metabarcoding samples that contain planktonic larvae from a given habitat, we could get an indication of which taxonomic group would benefit most from additional sampling effort or give an indication of the proportion of species that has not been sampled yet. Additionally, data generated by metabarcoding efforts can be re-interpreted as more DNA barcodes associated with correctly identified specimens become available. Building the library of DNA barcodes in parallel of metabarcoding efforts ensures that database matches correspond to actual specimens deposited in natural history collections, ruling out possible artifacts of the method. With such approaches, the geographic distribution of species can build on and be linked to existing records, species and their natural history, rather than being limited to matching DNA sequences across studies.

Assembling species lists is a necessary but not sufficient step in our quest to understand biodiversity. We also need to understand better the geographic distribution of biodiversity, how the abundance of species vary in space and time, and their role in the functioning of ecosystems. In order to predict the impact of climate change and other anthropogenic perturbations on species distributions, we need to collect additional occurrences for species as well as the characteristics of their habitats. Among the challenges of this enterprise, we need to be able to convey taxonomic concepts for species which, for the most part, have not formally been named yet. Developing robust identifiers that can be shared across biodiversity information systems, and anchored in results from DNA barcoding or other molecular techniques, is needed to collaboratively build our knowledge of species distributions.

@@

DNA sequences have been one of the first test case on how to link biodiversity data across repositories. These initial efforts have revealed the lack of infrastructure to use data formats specifically designed for this task, the lack of ontologies available for biodiversity data, and the fragility of the identifiers [@Stucky2014; @Walls2014; @Guralnick2014]. As new types of data will be collected, added, and linked across repositories, the community needs to develop modern and robust ways to integrate these heterogeneous biodiversity data sources [@Guralnick2015; @Deck2015].

Digitization efforts are catching up on already fragmented and incomplete records. Even if technological advances can greatly speed up the documentation of species and their distributions, taxonomists and experts are needed  to collect, sort, process, and identify samples. Taxonomic expertise within the US is dwindling, and there are now only a handful of US natural history museums with active marine invertebrates collections. This lack of resources is not sustainable in the face of the challenges and discoveries that marine ecosystems have to offer.

Crowd-sourced data and citizen science initiatives have been proposed to augment data about species abundance and distributions [@Pimm2014]. Beyond the application to near-shore habitats on easily recognizable species [@Delaney2008], large-scale efforts are currently not possible for marine ecosystems given the specialized equipment needed to sample most habitats and the expertise required to identify species. There are however opportunities for citizen science to help curate biodiversity data, while educating and engaging the public with marine conservation issues. For instance citizen science has been used successfully to classify plankton images [@Robinson2017], or transcribe hand-written museum labels [@Hill2012].

Here, we reported results from the US where there is at least two centuries of biodiversity exploration data and high-levels of digitization of museum collections. Many other parts of the world need additional attention, especially in some developing countries where environmental pressure on ecosystems is even higher than in the US.

>>>>

With increasing impact of human activities on the biosphere, we need efficient and accurate approaches to document changes in species ranges and community composition. <!-- add why? -->  While terrestrial ecosystems have received considerable attention, the baseline of healthy and resilient marine ecosystems is not well understood [@Worm2006], and modeling the impact of human activities has been limited to a few taxonomic groups [@Tittensor2010]. For marine organisms, because of the diversity of their complex life history strategies, their size range <!-- reformulate? -->, and the difficulties associated with sampling their habitats, we have limited information about which species live where, or what portion of their diversity remains to be discovered and described [@Mora2011]. Additionally, coordinated marine ecosystem monitoring initiatives have been lacking [@Duffy2013,@Borja2016] (but are now getting organized, see MarineGEO [@Duffy2016marinegeo], MBON, and PISCO), making it difficult to monitor changes in species distributions and abundances. While most documented global extinctions of marine species are vertebrates, many other species may have been lost unnoticed because they were not known [@Sala2006]. There is therefore a pressing need to improve our knowledge of marine systems before their functioning is irreversibly altered, and species go extinct.

Research attempting to understand how much we know about marine biodiversity has focused on estimating the total number of species that inhabits the oceans, and which fraction of this diversity has been named [@Appeltans2012,@Costello2013]. Undoubtedly, the development of molecular methods to investigate species limits has reinvigorated taxonomy and contributed to elucidating cryptic species complexes [@Knowlton2000]. Thus, it has been argued that molecular data can speed up the enterprise of discovering and naming species [@Blaxter2016]. As species remain the most convenient unit to measure biological diversity, understanding how much has been done, how much remains to be done, and how we can speed up the description of species diversity is crucial. However, to understand the role of these species in their environment, we need to document their ecology [@Cernansky2017]. For instance, to be able to predict how their geographic ranges will be affected by global change, we need detailed information about their environmental requirements. Occurrence data for marine species could be used for environmental niche modeling of their geographic and bathymetric distributions but the number of species -- and therefore the proportion of all species -- for which we have enough data to do so is unknown.

Until very recently, our knowledge of biodiversity was scattered among heterogeneous sources (e.g. natural history collections, publications, expert knowledge), difficult to access, and therefore difficult to synthesize. The development of public databases for specimen records (e.g. iDigBio [@Page2015]), species occurrences (e.g., OBIS [@Zhang2002]), genetic data (e.g., GenBank [@Benson2013], BOLD [@Ratnasingham2007a]), and registers of species names (e.g., WoRMS [@Costello2013b]) now allow us to evaluate what and how much we know. However, few studies have sought to synthesize existing knowledge by combining information from these databases.  Here, we aggregate publicly available data for marine invertebrates that occur within the limits of the exclusive economic zone (EEZ) of the continental United States (US), as well as the Gulf of Mexico (GOM) and the Pacific Northwest (PNW), to highlight gaps in our knowledge that provide a road map for important new directions in global research. We show that while public databases are capturing a significant portion of our knowledge about species richness, most species are known from only a few specimens and a few locations. We emphasize that our understanding of marine biodiversity, and the impact of human activities on biological communities require not only a more accurate list of the species that inhabit the oceans, but also more comprehensive data on species distributions and abundances. These goals can only be achieved with additional cost-effective sampling and a commitment to training more taxonomists and experts that can identify and interpret the material collected.

@@

We retrieved `r format(n_distinct(combined_species$worms_valid_name), big.mark = ",")` species (`r n_distinct(na.omit(combined_species$worms_phylum))` phyla) of marine invertebrates in the continental US EEZ by combining  `r format(nrow(idigbio_records), big.mark=",")` museum records from iDigBio (`r format(n_distinct(idigbio_records$worms_valid_name), big.mark = ",")` species, `r n_distinct(na.omit(idigbio_records$worms_phylum))` phyla), and `r format(nrow(obis_records), big.mark=",")` records from OBIS (`r format(n_distinct(obis_records$worms_valid_name), big.mark=",")` species,
`r n_distinct(na.omit(obis_records$worms_phylum))` phyla). Extant marine invertebrates occurring in the US represent less than 0.4% of the total number of iDigBio records (104+ million), and about 1% of the US records (33 million records). Marine invertebrates that occur in the US represent approximately 4% of the 48 million occurrence records in OBIS.

@@

Spatial distribution of species richness with latitude differ markedly between the Pacific and the Atlantic coasts. On the Pacific coast, richness is lowest around 40° of latitude, whereas on the Atlantic coast, it is highest at the same latitude (Fig. \@ref(fig:map-diversity-sampling)B, Fig. \@ref(fig:latitudinal-gradient)).

@@

```{r correlation-sampling, fig.cap='Relation between number of records and number of species for each cell of the map used in Fig. \\@ref(fig:map-diversity-sampling). The black line represents the 1:1 relationship. (\\#fig:correlation-sampling)'}
knitr::include_graphics("figures/plot_sampling_effort.pdf")
```

<!-- The median number of cells occupied by species is `r median(rastercell_distribution$n_cell)`. -->

@@

Environmental conditions are among the primary determinants of species distributions and can thus be used to estimate the response of organisms to climate change. Predictive ecological models forecasting changes in distributions are trained on environmental conditions encountered by species in their current distributions. To obtain reliable results, models require at least 10, but ideally 30 or more occurrence records per species [@Wisz2008]. Yet at present, `r prop_10_specimens_species`% of species are represented by $\leq$ 10 records, and `r prop_30_specimens_species`%  by $\leq$ 30 records based on the combined records in iDigBio and OBIS. Additionally, `r format_output(prop_missing_depth$p_missing * 100)`% ($n=$ `r format(prop_missing_depth$n_total, big.mark=",")` OBIS records) of the observations lack bathymetric information. Underscoring the inadequacy of the sampling effort, `r prop_singleton_species`% of the species are known from a single record.

Another indication of the inadequacy of the sampling is the relationship between the number of collected specimens and the number of species recorded through time (Fig. \@ref(fig:idigbio-through-time)). Explorations in the late nineteenth century led to an exponential growth in the knowledge of the fauna, but collecting then tapered off, until the 1970s when intensive collecting efforts led to an increase in the recording of new taxa (Fig. \@ref(fig:idigbio-through-time)). Since then, the slowed pace of collection activitity (and therefore a reduction in the number of specimens added) has been accompanied by a slow-down in the discovery of new records: `r n_spp_comparison$n_spp_2017_2000` species have been documented for the first time since 2000 (`r format_output(n_spp_comparison$n_spp_2017_2000/18)` species.year^-1^), while `r n_spp_comparison$n_spp_1970_1960` were documented between 1960 and 1970 (`r format_output(n_spp_comparison$n_spp_1970_1960/11)` species.year^-1^). The strong correlations between (1) the number of samples collected and the species richness (Fig. \@ref(fig:correlation-sampling)), and (2) the number of specimens collected per year and the number of species recorded for the first time (Fig. \@ref(fig:idigbio-through-time)C), suggest that any new sampling effort will lead to new observations and the discovery of new species.

```{r idigbio-through-time, fig.cap='Cumulative number of samples (A) and species (B) of marine invertebrates recorded through time based on iDigBio records. Relationship between number of samples collected, and number of species recorded for the first time (C), each point represents numbers for a given year, dashed line shows the 1:1 and dotted line the 1:100 ratios for number of species recorded for the first time to the number of samples. (\\#fig:idigbio-through-time)'}
knitr::include_graphics("figures/idigbio_through_time.pdf")
```

Further biases exist across phyla and body size. Large-bodied and easily accessible (e.g. dried specimens like shells, corals, echinoderms) specimens are over-represented in museum collections, compared with small less accessible organisms, such as the meiofauna. Of `r n_idigbio_phyla` phyla represented in iDigBio, `r records_rare_phyla$n_rare_phyla` have <500 records, and make up `r records_rare_phyla$prop_recs_rare_phyla`% of the iDigBio records. This under-representation is also manifested at the species level, while `r records_rare_phyla$prop_spp_rare_phyla_collected`% (n = `r format(records_rare_phyla$total_spp_rare_phyla_collected, big.mark=",")` total species) of the global number of species for these `r records_rare_phyla$n_rare_phyla` phyla occur in iDigBio, this proportion rises to `r records_rare_phyla$prop_spp_common_phyla_collected`% (n = `r format(records_rare_phyla$total_spp_common_phyla_collected, big.mark=",")`) for the `r n_idigbio_phyla - records_rare_phyla$n_rare_phyla` others. Yet, these undersampled taxa, especially those of small body size, are often the most abundant, and are likely to play an important role in the detection of changes in environmental quality[@Bik2012]. Additionally, the ecological implications of changes in the structure and composition of the communities of these small-bodied organisms, on higher trophic levels and ecosystems are largely unexplored.

@@

```{r id_though_time, fig.cap='Proportion of marine invertebrate specimens collected through time identified at the species level. Trend lines are  B-splines of the 3rd degree polynomial. For all groups, we observe a decline in the proportion of specimens collected that are identified at the species level, suggesting a lack of expertise to identity precisely what is collected. (\\#fig:identification-through-time)'}
knitr::include_graphics("figures/idigbio_identification_level_through_time.pdf")
```

@@

Since its introduction in the early 2000s, DNA barcoding has revitalized invertebrate taxonomy by facilitating species delineation [@Meyer2005-plos]. More recently, advances in high-throughput sequencing technologies have enabled the parallel sequencing of thousands of specimens in environmental samples (eDNA) cost effectively [@Leray2015], making it possible to estimate diversity and identify taxa from species-rich samples at unprecedented scales. With decreasing sequencing costs, and the prospect of automating sample collection, these technologies may soon be used routinely to monitor biodiversity continuously [@Bohan2017]. However, the utility of the data generated by these projects is limited by the paucity of reliably identified DNA barcode sequences that can serve for matching and identification of eDNA transcripts [@Leray2015]. Thus insights from eDNA technologies depend on the level of completeness and accuracy of comparative, species-level DNA barcode coverage.

@@

Based on the results of this study, we recommend a multi-level approach for both improving the quality of existing data and for the efficient collection of new data.

@@

With data aggregation of natural history collections through initiatives like iDigBio, and the compilation of a nearly complete register of marine species with WoRMS, in combination with the development of algorithms for text analysis, it is increasingly easier to validate and spell check the scientific names of the identifications of digitized museum specimens. Linking species names to identifiers in taxonomic databases would facilitate data linking, specimen discoverability, and data usability. Additionally, because registers of species names, such as WoRMS, link the history of the names and their synonymies, it is possible to dissociate the concepts of species identification with the concept of species identity, allowing researchers to compare specimens identified at different time periods.

@@

For both the spelling of scientific names, and the geographic information, computing tools can be developed to detect issues and provide solutions. There are opportunities to develop computing services that use publicly available data to flag and fix these issues directly from collection databases records (e.g. see [@Otegui2016] for vertebrate records). Such services, however, require that resources be made available to museum collections in order to address these issues directly in collection databases.

Increasing the computing literacy and teaching "data wrangling" skills to staff of museums in order for them to manipulate and use the data from their collection database is equally critical. As data across institutions are incorporated and pooled into large biodiversity information systems, it is crucial that data standards such as Darwin Core are embraced by the community.

@@

Museum specimens are critical for validating the occurrence of species [@Rocha2014], especially for marine invertebrates for which species limits based on morphology have been known to be challenged by other lines of evidence including molecular data [@Knowlton2000].

This study highlights that we have too little data about too few species of marine invertebrates. We recommend that additional coordinated field expeditions be organized to sample more comprehensively the marine environment. The relationship between sampling effort and diversity from museum collections makes clear that any additional samples will greatly improve our knowledge of marine biodiversity. Concerted and collaborative efforts are needed to share expertise and limited resources.

Samples collected during these expeditions need to be photographed to document live appearance, information that would otherwise be lost during the preservation process. We also need to capture metadata associated with specimens to be able to understand better the physical characteristics of the habitats and the life histories of these species. Specimens need to be sub-sampled to create material suitable for genomic analysis. Parts of data acquisition associated with specimens and their biota can be automated and captured digitally directly in the field, speeding up their ingestion in database collections.

Integrating metabarcoding as part of the data collection conducted in biodiversity surveys is a promising approach to screen an habitat for its potential to lead to new discoveries. For instance, by analyzing metabarcoding samples that contain planktonic larvae from a given habitat, we could get an indication of which taxonomic group would benefit most from additional sampling effort or give an indication of the proportion of species that has not been sampled yet. Additionally, data generated by metabarcoding efforts can be re-interpreted as more DNA barcodes associated with correctly identified specimens become available. Building the library of DNA barcodes in parallel with metabarcoding efforts ensures that database matches correspond to actual specimens deposited in natural history collections, ruling out possible artifacts of the method. With such approaches, the geographic distribution of species can build on and be linked to existing records, species and their natural history, rather than being limited to matching DNA sequences across studies.

Assembling species lists is a necessary but not sufficient step in our quest to understand biodiversity. We also need to understand better the geographic distribution of biodiversity, how the abundance of species varies in space and time, and species' roles in the functioning of ecosystems. In order to predict the impact of climate change and other anthropogenic perturbations on species distributions, we need to collect additional occurrences for species as well as the characteristics of their habitats. Among the challenges of this enterprise, we need to be able to convey taxonomic concepts for species that, for the most part, have not formally been named yet. Developing robust identifiers that can be shared across biodiversity information systems, and anchored in results from DNA barcoding or other molecular techniques, is needed to collaboratively build our knowledge of species distributions.

@@

DNA sequences are an early test case on how to link biodiversity data across repositories. These initial efforts have revealed the lack of infrastructure for using data formats specifically designed for this task, the lack of ontologies available for biodiversity data, and the fragility of the identifiers [@Stucky2014; @Walls2014; @Guralnick2014]. As new types of data will be collected, added, and linked across repositories, the community needs to develop modern and robust ways to integrate these heterogeneous biodiversity data sources [@Guralnick2015; @Deck2015].

Digitization efforts are catching up on already fragmented and incomplete records. Even if technological advances can greatly speed up the documentation of species and their distributions, taxonomists and experts are needed  to collect, sort, process, and identify samples. Taxonomic expertise within the US is dwindling, and there are now only a handful of US natural history museums with active collections of marine invertebrates. This lack of resources is not sustainable in the face of the challenges and discoveries that marine ecosystems have to offer.

Crowd-sourced data and citizen science initiatives have been proposed to augment data about species abundance and distributions [@Pimm2014]. Beyond the application to near-shore habitats on easily recognizable species [@Delaney2008], large-scale efforts are currently not possible for marine ecosystems given the specialized equipment needed to sample most habitats and the expertise required to identify species. There are however opportunities for citizen scientists to help curate biodiversity data, while educating and engaging the public with marine conservation issues. For instance citizen science has been used successfully to classify plankton images [@Robinson2017], and to transcribe hand-written museum labels [@Hill2012].

Here, we reported results from the US where there are at least two centuries of data on biodiversity exploration data and high-levels of digitization of museum collections. Many other parts of the world need additional attention, especially in some developing countries where environmental pressure on ecosystems is even higher than in the US.
